---
title: "Data analysis"
author: "Juliano Palacios Abrantes & William W.L. Cheung"
date: "2023-07-03"
output: pdf_document
---


```{r setup, results='hide', message=FALSE, echo = F}
library(MyFunctions)

packages <- c(
  "readxl", # Read dataframe
  "tidyverse", # for all data wrangling and ggplot
  "janitor", # for data cleaning
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "rnaturalearth", # For maps
  "doParallel",
  "foreach"
)

my_lib(packages)

# Fix new updates of sf package
sf::sf_use_s2(use_s2 = FALSE)
```

# Overall

This script uses the DBEM runs with the CMIP6 Earth System Models (GFDL, IPSL, MPIS) under SSP 126 and 585 to estimate the percentage change in each species maximum catch potential (MCP). The calculation is made by species in each EEZ and the output is a yearly percentage change relative to today starting from 2020.

# Select species

Here we will select the species to analyzed based on the plataform requirements, From Sarah:

- Global for tunas. 
- Alaska cod, they might also extend into other EEZs in the Arctic. 
- Anchovy, I thought we could include all species in the family Engraulidae. 


## Get EEZs

```{r select_eezs, eval = T, echo = T}

# selected_countries <- c(
  # "Peru",
  # "Chile"
# )

# Read SAU EEZs
sf_sau_eez <- MyFunctions::my_sf("SAU") %>% 
  clean_names()

# Get EEZ names
# sf_sau_eez %>%
#   as.data.frame() %>%
#   select(name) %>%
# View()


sf_region <-
  sf_sau_eez %>% 
  filter(name %in% selected_countries)
  
unique(sf_region$name)
  
length(unique(sf_region$name))

# write_csv(sf_region %>% as.data.frame() %>% select(-geometry),
      # "../data/spatial/region_index.csv")

# Visually make sure
sf_region %>%  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>% 
  st_shift_longitude() %>%
  ggplot() +
  geom_sf(aes())

```

## Get speceis list

We selected all species captured since 2006 within the EEZs of the region. Such species represent 66% of the identified species fished since 2006

```{r select_spp, eval = T, echo = T}

# Read species list

exploited_species_list <- read_csv("~/Library/CloudStorage/OneDrive-UBC/Data/Species/exploited_species_list.csv")

spp_selected <- c("Thunnus albacares",
                  "Katsuwonus pelamis",
                  "Engraulis albidus",
                  "Engraulis anchoita",
                  "Engraulis australis",
                  "Engraulis capensis ",
                  "Engraulis encrasicolus",
                  "Engraulis eurystole",
                  "Engraulis japonicus",
                  "Engraulis mordax",
                  "Engraulis ringens",
                  "Gadus macrocephalus"
                  )


# Read species list
spp_list <- exploited_species_list %>% 
  janitor::clean_names() %>% 
  filter(taxon_name %in% spp_selected)

# Save complete list
# write_csv(spp_list,"../data/species/project_spplist.csv")

```

## Main analysis

We projected the distribution of species using the DBEM coupled with three Earth System Models (ESMs) following two Shared Socioeconomic Pathways (SSPs); SSP 126 representing a low emission / high mitigation scenario and SSP 585 representing a high emission / no mitigation scenario. 

For each species, we projected its future maximum catch potential or "MCP" (a proxy of MSY) within each EEZ from 1951 to 2100. We then determined a present time period representing the average projections from 1995 to 2014 to match the historical data used by the ESMs. For each subsequent year, we estimate the percentage change in MCP ($\Delta{MCP}$) as:


$$\Delta{MCP} =\frac{MCP_f-MCP_p}{MCP_p}*100$$
Where $MCP_f$ represents the future years and $MCP_p$ represents the current time period. As an arbitrary rules, if $MCP_p$ = 0 & $MCP_f$ > 0 then ($\Delta{MCP}$) = 100, and if $MCP_p$ > 0 & $MCP_f$ < 0 then ($\Delta{MCP}$) = -100.


### Function needed

```{r main_fx, eval = F, echo = T}

mainfx <- function(taxon){
  
  to_read <- paste0(taxon,"MCP.RData")
  
  for(m in 1:6){
    
    #################################
    # List esm folders
    file_to_read <- paste0(files_path[m],"/",to_read)
    
    if(file.exists(file_to_read)){
      load(file_to_read)
      
      # Transform it to df
      spp_data <- as.data.frame(sppMCPfnl) %>% 
        rowid_to_column("index")
        
      colnames(spp_data) <- c("index",(seq(1951,2100,1)))
      rm(sppMCPfnl) # remove data for computing power
      
      early_data <- spp_data %>% 
        gather("year","value",`1951`:`2100`) %>% 
        mutate(period = ifelse(year < 2014 & year > 1995,"present",NA)) %>% 
        filter(!is.na(period)) %>% 
          left_join(regional_grid,
                    by = "index") %>%
          filter(!is.na(eez_id)) %>%
        group_by(eez_name,year,period) %>% 
        # Sum total catch per eez per year
        summarise(eez_catch = sum(value, na.rm = T),.groups = "drop") %>% 
        group_by(eez_name,period) %>% 
        # Average yearly data
        summarise(mean_catch = mean(eez_catch,na.rm = T),.groups = "drop")
      
      # Estimate percentage change
      future_data <-  spp_data %>% 
        gather("year","value",`1951`:`2100`) %>% 
        filter(year > 2004) %>% 
        left_join(regional_grid,
                  by = "index") %>%
        filter(!is.na(eez_id)) %>%
        group_by(eez_name,year) %>% 
        # Sum total catch per eez per year
        summarise(eez_catch = sum(value, na.rm = T),.groups = "drop") %>% 
        left_join(early_data,
                  by = "eez_name") %>%
        # spread(period,mean_catch) %>% 
        mutate(
          per_change = ifelse(mean_catch == 0 & eez_catch > 0,100, 
                              round((eez_catch-mean_catch)/mean_catch*100)
          ),
          species = taxon
        ) %>% 
        group_by(species,eez_name) %>% 
        mutate(
          per_change_rm = round(zoo::rollmean(
            per_change,
            k = 10, 
            fill = NA, 
            align = "right")
          )
        ) %>% 
        filter(!is.na(per_change_rm)) %>%
        select(species,eez_name,year,per_change_rm)
      
      # Visualization
      # ggplot() +
      #   geom_line(data = future_data,
      #     aes(
      #       x = as.numeric(year),
      #       y = per_change_rm,
      #       color = eez_name
      #     )
      #   ) +
      #   scale_color_viridis_d("EEZ",option = "I") +
      #   my_ggtheme_p() +
      #   labs(
      #     x= "Year",
      #     y = "Change Relative to Historical Value (%)"
      #     )
      
      # Join data for all three models
      if(m == 1){
        partial_output <- future_data
      }else{
        partial_output <- bind_rows(partial_output,future_data)
      }
      
      
      final_output <- partial_output %>% 
        group_by(species,eez_name,year) %>% 
        summarise(mean_per_change = mean(per_change_rm, na.rm =T),
                  sd_per_change = sd(per_change_rm, na.rm =T))
      
      
      spp_name <- spp_list %>% filter(taxon_key %in% taxon) %>% pull(common_name)
      name <- paste0(spp_name,".csv")
      
      write_csv(final_output,
                my_path("R","Raw",name))
      
    }else{
      return(print(paste("something went wrong with",taxon_key,
                         str_to_lower(str_sub(files_path[m],49,56)))))
    }
  }
  
} # Close function

```

### Control panel

```{r protocol_control_panel, eval = F, echo = T}

# Get species list
# spp_list <- read_csv("../data/species/project_spplist.csv")

par_spp_list <- spp_list %>% 
  pull(taxon_key)

# Get DBEM coords
dbem_coords <- my_data("dbem_coords")

# Get the regional grid 
# region_index <- read_csv("../data/spatial/region_index.csv") 

# Get list of index by EEZ
# eez_grid_id <- my_path("Spa","DBEM", "EEZ_CellID.xlsx", read = TRUE)
# colnames(eez_grid_id) <- c("eez_id","index")

eez_grid_id <- my_data("sau_index")

regional_grid <- eez_grid_id #%>%
  # filter(eez_id %in% sf_region$eezid)

# Get the DBEM path
files_path <- my_path("G","dbem/dbem_cmip6/r_data/C6GFDL85F1_t2")

```


### Run protocol (Parallel)

```{r run_protocol, eval = F, echo = T}
# get the cores from your computer.
# No need for more than 12 cores 
# Never use all cores so you computer doesn't crash
# cores <- ifelse(detectCores() > 12, 12, detectCores()-6)  
# cl <- makeCluster(cores[1])
# registerDoParallel(cl)
# 
# 
# run <- foreach(i = 1:length(par_spp_list), .packages = "tidyverse") %dopar% {
#   mainfx(par_spp_list[i])
# }
# 
# stopCluster(cl)
# gc()

suppressWarnings(
lapply(par_spp_list, mainfx)
)
```

# Test runs

Testing results for a taxon to make sure all EEZs are included

```{r test_result, eval = T, echo = T}
#  Note you need to run firt two chunks

# Load result test
result_df <- read_csv("~/Data/ocea_nutri_cc/results/600107_per_change.csv")

unique(result_df$esm) #c6gfdl

unique(result_df$ssp) # "ssp26" "ssp85"

summary(result_df)
```


```{r test_result_map, eval = T, echo = T}

sf_region %>%  
  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>% # Picaso style map to load faster
  st_shift_longitude() %>% # Center projection on Pacific Islands
  rename(eez_id = eezid) %>% # To mathc SAU shapefile
  left_join(result_df) %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = per_change_mid
    )
  ) + facet_wrap(~ssp, ncol = 1) +
  scale_fill_gradient2()
  



```







	