---
title: "Data Outputs for Ocean Future Project"
subtitle: "Juliano Palacios Abrantes & William W.L. Cheung"
author: "Contact: j.palacios@oceans.ubc.ca"
date: "2023-08-15"
output: pdf_document
editor_options: 
  chunk_output_type: inline
---


```{r setup, results='hide', message=FALSE, echo = F}
library(MyFunctions)

packages <- c(
  "readxl", # Read dataframe
  "tidyverse", # for all data wrangling and ggplot
  "janitor", # for data cleaning
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "rnaturalearth", # For maps
  "doParallel",
  "foreach",
  # For netcdf files
  "ncdf4",
  "metR"
)

my_lib(packages)

# Fix new updates of sf package
sf::sf_use_s2(use_s2 = FALSE)
```


```{r}
track_time <- function(category = "day") {
  
  # Load/Create timesheet
  path_to_read <- MyFunctions::my_path("D",name = "project_time_count.csv")
  
  if(category == "day"){
    
    start_time <- Sys.time()
    message("Tracking time started.")
    on.exit({
      end_time <- Sys.time()
      time_spent <- end_time - start_time
      message("Time spent on the project:", time_spent)
      
      # Create time data frame
      df <- data.frame(Start_Time = as.character(start_time), End_Time = as.character(end_time), Time_Spent = as.numeric(time_spent))
      
      if(file.exists(path_to_read)){
        time_df <- dplyr::bind_rows(read.csv(path_to_read),
                                    df)
        
      }else{
        
        time_df <- data.frame(Start_Time = start_time, End_Time = end_time, Time_Spent = time_spent)
      }
      
      # Save the data frame to a file
      write.csv(time_df, path_to_read, row.names =  F)  
      
    })
  }
}

track_time()
```


# Overall

This script uses the DBEM runs with the CMIP6 Earth System Models (GFDL, IPSL, MPIS) under SSP 126 and 585 to estimate the percentage change in each species maximum catch potential (MCP). The calculation is made by species in each EEZ and the output is a yearly percentage change relative to today starting from 2014.

# Species selection

Climate change projections for the following species were requested to be used in the project:

- Global for tunas. 
  - *Thunnus albacares*
  - *Katsuwonus pelamis*

- Alaska cod, they might also extend into other EEZs in the Arctic. 

  - *Gadus macrocephalus*

- Anchovy, I thought we could include all species in the family Engraulidae. 
  - *Engraulis albidus*
  - *Engraulis anchoita*
  - *Engraulis australis*
  - *Engraulis capensis* 
  - *Engraulis encrasicolus*
  - *Engraulis eurystole*
  - *Engraulis japonicus*
  - *Engraulis mordax*
  - *Engraulis ringens*


<!-- ## Get EEZs -->

```{r select_eezs, eval = F, echo = F}

# selected_countries <- c(
  # "Peru",
  # "Chile"
# )

# Read SAU EEZs
sf_sau_eez <- MyFunctions::my_sf("SAU") %>% 
  clean_names()

# Get EEZ names
# sf_sau_eez %>%
#   as.data.frame() %>%
#   select(name) %>%
# View()


sf_region <-
  sf_sau_eez %>% 
  filter(name %in% selected_countries)
  
unique(sf_region$name)
  
length(unique(sf_region$name))

# write_csv(sf_region %>% as.data.frame() %>% select(-geometry),
      # "../data/spatial/region_index.csv")

# Visually make sure
sf_region %>%  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>% 
  st_shift_longitude() %>%
  ggplot() +
  geom_sf(aes())

```

Here we filter our model runs to the selected species. There are eight species in our data set from those originally requested.

```{r select_spp, eval = T, echo = F, message = F, warning = F}

# Read species list

exploited_species_list <- read_csv("~/Library/CloudStorage/OneDrive-UBC/Data/Species/exploited_species_list.csv")

spp_selected <- c("Thunnus albacares",
                  "Katsuwonus pelamis",
                  "Engraulis albidus",
                  "Engraulis anchoita",
                  "Engraulis australis",
                  "Engraulis capensis ",
                  "Engraulis encrasicolus",
                  "Engraulis eurystole",
                  "Engraulis japonicus",
                  "Engraulis mordax",
                  "Engraulis ringens",
                  "Gadus macrocephalus"
                  )


# Read species list
spp_list <- exploited_species_list %>% 
  janitor::clean_names() %>% 
  filter(taxon_name %in% spp_selected)

# Save complete list
# write_csv(spp_list,"../Data/project_spplist.csv")

head(spp_list,8)
```

## Main analysis

We projected the distribution of species using the DBEM coupled with three Earth System Models (ESMs) following two Shared Socioeconomic Pathways (SSPs); SSP 126 representing a low emission / high mitigation scenario and SSP 585 representing a high emission / no mitigation scenario. 

For each species, we projected its future maximum catch potential or "MCP" (a proxy of MSY - See reference documents) within each EEZ from 1951 to 2100. We then determined a present time period representing the average projections from 1995 to 2014 to match the historical data used by the ESMs. For each subsequent year, we estimate the percentage change in MCP ($\Delta{MCP}_y$) as:


$$\Delta{MCP}_y =\frac{MCP_f-MCP_p}{MCP_p}*100$$
Where $MCP_f$ represents the future years and $MCP_p$ represents the current time period. As an arbitrary rules, if $MCP_p$ = 0 & $MCP_f$ > 0 then ($\Delta{MCP}$) = 100, and if $MCP_p$ > 0 & $MCP_f$ < 0 then ($\Delta{MCP}$) = -100. 

The results for each species and SSP was first average by ESM $\pm$ s.d. to account for structural differences among models and then average by 10 years blocks (i.e., running average) to reduce the temporal (natural) variability of the system (See reference documentation).

### Function needed

See the [GitHub](https://github.com/jepa/ocean_future) repository for code details.

```{r main_fx, eval = F, echo = F}

mainfx <- function(taxon){
  
  
  # List esm folders
  scenrios <- list.files("~/Library/CloudStorage/OneDrive-UBC/Data/dbem/dbem_cmip6/r_data",full.names = T)
  to_read <- paste0(taxon,"MCP.RData")
  
  for(m in 1:6){
    
    file_to_read <- paste0(scenrios[m],"/",to_read)
    if(file.exists(file_to_read)){
      
      load(file_to_read)
      
      # Transform it to df
      
      if(exists("sppMCPfnl", envir = .GlobalEnv) == TRUE){
        
        spp_data <- as.data.frame(sppMCPfnl) %>% 
        rowid_to_column("index")
        
        colnames(spp_data) <- c("index",(seq(1951,2100,1)))
      rm(sppMCPfnl) # remove data for computing power
        
      }else{
        
        spp_data <- as.data.frame(data) %>% 
        rowid_to_column("index")
        colnames(spp_data) <- c("index",(seq(1951,2100,1)))
        rm(data) # remove data for computing power
      }
      
      
      
      early_data <- spp_data %>% 
        gather("year","value",`1951`:`2100`) %>% 
        mutate(period = ifelse(year < 2014 & year > 1995,"present",NA)) %>% 
        filter(!is.na(period)) %>% 
        left_join(regional_grid,
                  by = "index") %>%
        filter(!is.na(eez_id)) %>%
        group_by(eez_name,year,period) %>% 
        # Sum total catch per eez per year
        summarise(eez_catch = sum(value, na.rm = T),.groups = "drop") %>% 
        group_by(eez_name,period) %>% 
        # Average yearly data
        summarise(mean_catch = mean(eez_catch,na.rm = T),.groups = "drop")
      
      # Estimate percentage change
      future_data <-  spp_data %>% 
        gather("year","value",`1951`:`2100`) %>% 
        filter(year > 2004) %>% 
        left_join(regional_grid,
                  by = "index") %>%
        filter(!is.na(eez_id)) %>%
        group_by(eez_name,year) %>% 
        # Sum total catch per eez per year
        summarise(eez_catch = sum(value, na.rm = T),.groups = "drop") %>% 
        left_join(early_data,
                  by = "eez_name") %>%
        # spread(period,mean_catch) %>% 
        mutate(
          per_change = ifelse(mean_catch == 0 & eez_catch > 0,100, 
                              round((eez_catch-mean_catch)/mean_catch*100)
          ),
          species = taxon
        ) %>% 
        filter(!is.na(per_change)) %>% 
        select(species,eez_name,year,per_change) %>% 
        mutate(
          esm = str_sub(file_to_read,79,82),
          ssp = ifelse(str_sub(file_to_read,83,84) == 26,"ssp126","ssp585")
        )
      
      
      
      # Join data for all three models
      if(m == 1){
        partial_output <- future_data
      }else{
        partial_output <- bind_rows(partial_output,future_data)
      }
      
    }else{
      partial_output
      print(file_to_read)
    }
  }
    
    print(paste(unique(partial_output$esm)))
    
    final_output <- partial_output %>% 
      group_by(species,eez_name,year,ssp) %>% 
      summarise(mean_per_change = mean(per_change, na.rm =T),
                sd_per_change = sd(per_change, na.rm =T)) %>% 
      group_by(species,eez_name,ssp) %>% 
      mutate(
        per_change_rm = round(zoo::rollmean(
          mean_per_change,
          k = 10, 
          fill = NA, 
          align = "right")
        )
      ) %>% 
      filter(!is.na(per_change_rm))
    
    
    spp_name <- spp_list %>% filter(taxon_key %in% taxon) %>% pull(common_name)
    name <- paste0(spp_name,".csv")
    
    write_csv(final_output,
              my_path("R","Raw",name))
    
    
} # Close function

```

### Control panel

Prepare data for running the protocol

```{r protocol_control_panel, eval = F, echo = F}

# Get species list
spp_list <- read_csv("./Data/project_spplist.csv")

par_spp_list <- spp_list %>% 
  pull(taxon_key)

# Get DBEM coords
dbem_coords <- my_data("dbem_coords")

# eez grid ID
regional_grid <- my_data("sau_index")

```


### Run protocol 

Run `mainfx` across species

```{r run_protocol, eval = F, echo = F}
# get the cores from your computer.
# No need for more than 12 cores 
# Never use all cores so you computer doesn't crash
# cores <- ifelse(detectCores() > 12, 12, detectCores()-6)  
# cl <- makeCluster(cores[1])
# registerDoParallel(cl)
# 
# 
# run <- foreach(i = 1:length(par_spp_list), .packages = "tidyverse") %dopar% {
#   mainfx(par_spp_list[i])
# }
# 
# stopCluster(cl)
# gc()

suppressWarnings(
lapply(par_spp_list[3], mainfx)
)
```


## Results

### Metadata

Each species has its own file in a `csv` format containing the average projections across ESMS by SSP on all EEZs where the specie is present. Each file contains the following structure:

- `species`, species code
- `eez_name`,  name of the EEZ according to The Sea Around Us (See www.searoundus.org). Note that sometimes a county's EEZ can be split in 2 or 3, for example Mexico Pacific and Mexico Atlantic
- `year`, Year or projection from 2014 to 2100
- ssp, Shared Socioeconomic Pathway according to the IPPC. ssp 126 represents a low emisison scenario and ssp 585 a high emisison scenario. (See https://www.dkrz.de/en/communication/climate-simulations/cmip6-en/the-ssp-scenarios)
- `mean_per_change`, mean percentage change from three Earth System Models
- `sd_per_change`, standard deviation percentage change from three Earth System Models
- `per_cahnge_rm`, 10 years running mean of the mean percentage change from three Earth System Models


### Test runs

Using Anchoveta in Chile Peru and Ecuador as an example of model outputs. 

```{r test_result, eval = T, echo = F}
#  Note you need to run firt two chunks

# Load result test
result_df <- my_path("R","ocean_future_projections","Anchoveta.csv", read = T)

head(result_df)
```


```{r test_result_map, eval = T, echo = F}

# Visualization
ggplot() +
  geom_line(data = result_df,
            aes(
              x = as.numeric(year),
              y = mean_per_change,
              color = eez_name
            )
  ) +
  geom_line(data = result_df,
            aes(
              x = as.numeric(year),
              y = per_change_rm,
              group = eez_name
            ),
            color = "black"
  ) +
  geom_ribbon(data = result_df,
              aes(
                x = as.numeric(year),
                ymax = per_change_rm+sd_per_change,
                ymin = per_change_rm-sd_per_change,
                fill = eez_name
              ),
              alpha = 0.5
  ) +
  scale_color_viridis_d("EEZ") +
  scale_fill_viridis_d("EEZ",) +
  my_ggtheme_p(ax_tx_s = 9,ax_tl_s = 10,leg_tl_s = 10,leg_tx_s = 10) +
  labs(
    x= "Year",
    y = "Change Relative to Historical Value (%)"
  ) +
  facet_wrap(~ssp)

# ggsave(
#   plot = last_plot(),
#   "../Results/Figures/example_figure_anchoveta.png",
#   width = 7,
#   height = 4
# )
```

# Aggregated version

The aggregated version is similar to the previous version with the exception that the results from all species is first aggregated by grid cell. This means that, for each ESM and SSP we first load each species data and aggregated the MCP of each gird cell from 1951 to 2100. After that, the steps are the same as before: first we estimated past and future MCP and then compute the % difference between these two.

## Control panel

Prepare data for running the protocol

```{r agg_pannel, eval = F, echo = F}

# List esm folders
scenarios <- as.data.frame( list.files("~/Library/CloudStorage/OneDrive-UBC/Data/dbem/dbem_cmip6/r_data",full.names = T))
colnames(scenarios) <- "path"

paths <- scenarios %>%  pull(path)

# Get species list
spp_list <- read_csv("./Data/project_spplist.csv")

par_spp_list <- spp_list %>% 
  pull(taxon_key)

to_read <- paste0(spp_list$taxon_key,"MCP.RData")
```

## Run protocol

Run `agg_n_fx` across models

```{r agg_protocol, eval = F, echo = F}


for(m in 1:nrow(scen)){
  
  file_to_read <- paste0(paths[m],"/",to_read)
  
  for(i in 1:length(file_to_read)){
    
    load(file_to_read[i])
    
    # Transform it to df
    
    if(exists("sppMCPfnl", envir = .GlobalEnv) == TRUE){
      
      spp_data <- as.data.frame(sppMCPfnl) %>% 
        rowid_to_column("index")
      
      colnames(spp_data) <- c("index",(seq(1951,2100,1)))
      rm(sppMCPfnl) # remove data for computing power
      
    }else{
      
      spp_data <- as.data.frame(data) %>% 
        rowid_to_column("index")
      colnames(spp_data) <- c("index",(seq(1951,2100,1)))
      rm(data) # remove data for computing power
    }
    
    
    partial_data <- spp_data %>% 
      gather("year","value",`1951`:`2100`) 
    
    # Join data for all three models
    if(i == 1){
      complete_output <- partial_data
    }else{
      
      complete_output <- left_join(complete_output,partial_data,
                                   by = c("index","year")
      ) %>% 
        mutate_at(
          .vars = c("value.x","value.y"),
          .funs = replace_na,0
        ) %>% 
        mutate(sum_value = value.x + value.y) %>% 
        select(index,year,value = sum_value)
      
    }
    
  } # close for loop in i for species
  
  
  # Estimate historical MCP data for all species
  early_data <- complete_output %>% 
    mutate(period = ifelse(year < 2014 & year > 1995,"present",NA)) %>% 
    filter(!is.na(period)) %>% 
    left_join(regional_grid,
              by = "index") %>%
    filter(!is.na(eez_id)) %>%
    group_by(eez_name,year,period) %>% 
    # Sum total catch per eez per year
    summarise(eez_catch = sum(value, na.rm = T),.groups = "drop") %>% 
    group_by(eez_name,period) %>% 
    # Average yearly data
    summarise(mean_catch = mean(eez_catch,na.rm = T),.groups = "drop")
  
  # Estimate percentage change in future data for all species
  future_data <-  complete_output %>% 
    filter(year > 2004) %>% 
    left_join(regional_grid,
              by = "index") %>%
    filter(!is.na(eez_id)) %>%
    group_by(eez_name,year) %>% 
    # Sum total catch per eez per year
    summarise(eez_catch = sum(value, na.rm = T),.groups = "drop") %>% 
    left_join(early_data,
              by = "eez_name") %>%
    # spread(period,mean_catch) %>% 
    mutate(
      per_change = ifelse(mean_catch == 0 & eez_catch > 0,100, 
                          round((eez_catch-mean_catch)/mean_catch*100)
      )
    ) %>% 
    filter(!is.na(per_change)) %>% 
    select(eez_name,year,per_change) %>% 
    mutate(
      esm = unique(str_sub(file_to_read,79,82)),
      ssp = unique(ifelse(str_sub(file_to_read,83,84) == 26,"ssp126","ssp585"))
    )
  
  # Join data for all three models
  if(m == 1){
    models_output <- future_data
  }else{
    models_output <- bind_rows(models_output,future_data)
  }
} # close for loop in m for models


# Average results per ESM
final_output <- models_output %>% 
  group_by(eez_name,year,ssp) %>% 
  summarise(mean_per_change = mean(per_change, na.rm =T),
            sd_per_change = sd(per_change, na.rm =T)) %>% 
  group_by(eez_name,ssp) %>% 
  mutate(
    per_change_rm = round(zoo::rollmean(
      mean_per_change,
      k = 10, 
      fill = NA, 
      align = "right")
    )
  ) %>% 
  filter(!is.na(per_change_rm))

# Save data
write_csv(final_output,
          my_path("R",name = "aggregated_data.csv"))

 
```


## Results

Structure of results is all the same except for the lack of a `species` column as these are all aggregated here.

## Test results

```{r test_agg_result, eval = T, echo = F}
#  Note you need to run firt two chunks

# Load result test
agg_df <- my_path("R","ocean_future_projections",name = "aggregated_data.csv", read = T)

head(agg_df)
```


```{r agg_plot, eval = T, echo = F}

agg_df %>% 
  filter(eez_name %in% c("Mexico (Pacific)","Mexico (Atlantic)","Peru","Chile")) %>% 
  ggplot() +
  geom_line(
    aes(
      x = as.numeric(year),
      y = mean_per_change,
      color = eez_name
    )
  ) +
  geom_line(data = agg_df %>% filter(eez_name %in% c("Mexico (Pacific)","Mexico (Atlantic)","Peru","Chile")),
            aes(
              x = as.numeric(year),
              y = per_change_rm,
              group = eez_name
            ),
            color = "black"
  ) +
  geom_ribbon(data = agg_df %>% filter(eez_name %in% c("Mexico (Pacific)","Mexico (Atlantic)","Peru","Chile")),
              aes(
                x = as.numeric(year),
                ymax = per_change_rm+sd_per_change,
                ymin = per_change_rm-sd_per_change,
                fill = eez_name
              ),
              alpha = 0.5
  )  +
  scale_color_viridis_d("EEZ") +
  scale_fill_viridis_d("EEZ",) +
  my_ggtheme_p(ax_tx_s = 9,ax_tl_s = 10,leg_tl_s = 10,leg_tx_s = 10) +
  labs(
    x= "Year",
    y = "% Change Relative to Historical Value\n(All species aggregated)"
  ) +
  facet_wrap(~ssp)

```


## All Species porotocol

### Get DBEM data 

```{r get_dbem_data, eval = F, echo = F}


# SAU index
sau_index <- my_data("sau_index")

dbem_index <- my_data("dbem_coords")


cdf_to_csv <- function(file){
  
  
  if(str_detect(file, "126")){
    ssp <- "126"
  }
  
  if(str_detect(file, "585")){
    ssp <- "585"
  }
  
  if(str_detect(file, "historical")){
    ssp <- "historical"
  }
  
  if(str_detect(file, "ipsl")){
    esm <- "ipsl"
  }else{
    esm <- "gfdl"
  }
  
  mem <- str_sub(file,81,84)
  
  
  df_out <- ReadNetCDF(file) %>%
    mutate(year = year(time)) %>% 
    filter(year > 1994) %>% 
    group_by(lat,lon,year) %>% 
    summarise_at("tcb",
                 mean,
                 na.rm = T) %>% 
    mutate(esm = esm,
           mem = mem,
           ssp = ssp)
  
  name <- paste0(my_path("R"),mem,"_",ssp,"_",esm,".csv")
  write_csv(df_out,name)
  
}

```


### Load data

```{r load_fishmip_data, eval = T, echo = F, message = F}

ssp <- "585"



# FishMip cmip6 data
historical_list <- list.files(my_path("R"),full.names = T, pattern = "historical")

hist_df <- bind_rows(
  lapply(historical_list, read_csv)
)

model_list <- list.files(my_path("R"),full.names = T)[1:4]

future_df <- bind_rows(
  lapply(model_list, read_csv)
  )


all_models <- bind_rows(hist_df,future_df %>% mutate(ssp = as.character(ssp)))

unique(all_models$mem)
unique(all_models$ssp)

# Joint all data needed

models_df <- all_models %>% 
  left_join(dbem_index, 
            by = c("lat","lon")
            ) %>% 
  left_join(sau_index,
            by = c("index")
            ) %>% 
  group_by(eez_name,esm,year,ssp) %>% 
  summarise(tcb = sum(tcb, na.rm = T)) %>% 
  filter(!is.na(eez_name))

unique(models_df$ssp)
length(unique(models_df$eez_name))

```

### Estimate prop. change

```{r}

# Estimate historical MCP data for all species
early_data <- models_df %>% 
  filter(ssp =="historical") %>% 
  group_by(eez_name) %>% 
  # Average yearly data
  summarise(h_mean_tcb = mean(tcb,na.rm = T),.groups = "drop")

# Estimate percentage change in future data for all species
future_data <-  models_df %>% 
  filter(ssp != "historical") %>% 
  left_join(early_data,
            by = c("eez_name")
  ) %>%
  # spread(period,mean_catch) %>% 
  mutate(
    per_change = ifelse(h_mean_tcb == 0 & tcb > 0,100, 
                        round((tcb-h_mean_tcb)/h_mean_tcb*100)
    )
  ) %>% 
  filter(!is.na(per_change)) %>% 
  group_by(eez_name,year,ssp) %>% 
  summarise(
    mean_per_change = mean(per_change, na.rm =T),
    sd_per_change = sd(per_change, na.rm =T)
  ) %>% 
  group_by(eez_name,ssp) %>% 
  mutate(
    per_change_rm = round(zoo::rollmean(
      mean_per_change,
      k = 10, 
      fill = NA, 
      align = "left")
    )
  ) %>% 
  filter(!is.na(per_change_rm))

# Save data
write_csv(future_data,
          my_path("R",name = "aggregated_data_all_spp.csv"))

```

### Test all species result

```{r}

future_data %>% 
  filter(eez_name %in% c("Mexico (Pacific)","Mexico (Atlantic)","Peru","Chile")) %>% 
  ggplot() +
  geom_line(
    aes(
      x = as.numeric(year),
      y = mean_per_change,
      color = eez_name
    )
  ) +
  geom_line(data = future_data %>% filter(eez_name %in% c("Mexico (Pacific)","Mexico (Atlantic)","Peru","Chile")),
            aes(
              x = as.numeric(year),
              y = per_change_rm,
              group = eez_name
            ),
            color = "black"
  ) +
  geom_ribbon(data = future_data %>% filter(eez_name %in% c("Mexico (Pacific)","Mexico (Atlantic)","Peru","Chile")),
              aes(
                x = as.numeric(year),
                ymax = per_change_rm+sd_per_change,
                ymin = per_change_rm-sd_per_change,
                fill = eez_name
              ),
              alpha = 0.5
  )  +
  scale_color_viridis_d("EEZ") +
  scale_fill_viridis_d("EEZ",) +
  my_ggtheme_p(ax_tx_s = 9,ax_tl_s = 10,leg_tl_s = 10,leg_tx_s = 10) +
  labs(
    x= "Year",
    y = "% Change Relative to Historical Value\n(All species aggregated)"
  ) +
  facet_wrap(~ssp)

```



# References

- Cheung, W. W. L.,*et al.*, 2009. Projecting global marine biodiversity impacts under climate change scenarios. Fish and Fisheries, 10 (3), 235–251.

- Cheung, W. W. L.,*et al.*, 2016. Structural uncertainty in projecting global fisheries catches under climate change. Ecological Modelling, 325, 57–66.

- Frölicher, T. *et al.*, 2016. Sources of uncertainties in 21st century projections of potential ocean ecosystem stressors. Global Biogeochemical Cycles [online], 30 (8), 1224–1243.

- Tittensor, D. P., *et al.*, 2021. Next-generation ensemble projections reveal higher climate risks for marine ecosystems. Nature Climate Change, 11 (11), 973–981.
