---
title: "Data for Jessica G. on Trade Analysis"
author: "Juliano Palacios-Abrantes"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, results='hide', message=FALSE, echo = F}

library(MyFunctions)

packages <- c(
  "readxl", # Read dataframe
  "tidyverse", # for all data wrangling and ggplot
  "janitor", # for data cleaning
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "rnaturalearth", # For maps
  "doParallel",
  "foreach",
  # For netcdf files
  "ncdf4",
  "metR",
  "readr",
  "taxize"
)

my_lib(packages)

# Fix new updates of sf package
sf::sf_use_s2(use_s2 = FALSE)
```

# Overall

Based on your suggestions I will work in the following three approaches to average of the species that we have information for within the higher taxa within:

0 - All species in the world
1- All the species captured in the EEZ 
2- Captured in the EEZ weighted by capture tonnage 
3- Captured within the a large marine ecosystem (LME). I think this would be more straightforward than making a step-by-step expansion across EEZs


# Data

```{r}

# SAU Catch Data 

# SAUCatch_FE_EEZ_FAO_taxa_sector_29May2020 
sau_catch <- read_csv("~/Library/CloudStorage/OneDrive-UBC/Data/sau/catch_data/SAUCatch_FE_EEZ_FAO_taxa_sector_29May2020.csv")


# Jessica's species list
# artis_spp <- my_path("D","jg","jessica_sau_taxa.csv", read = T) %>% 
#   rename(
#          a_common_name = common_name,
#          a_genus = genus) %>% 
#   mutate(taxon_name = str_to_sentence(sci_name)) %>% 
#   left_join(sau_spp)

# DBEM species list
dbem_spp <- my_data("dbem_species") %>% 
  mutate(dbem = 1)

# dbem_catch <- sau_catch %>% 
#   filter(taxon_key %in% dbem_spp$taxon_key)


# SAU spp list
sau_spp <- my_path("Species","updated_data/sau_updated_data/","TaxonNom_v42.1_151113.xlsx", read = T) %>% 
  left_join(dbem_spp)

```

## Get all species catched by EEZ

```{r}

# Get SAU taxon per EEZ
sau_taxon_eez <- sau_catch %>% 
  group_by(eezid,taxon_key) %>% 
  tally() %>% 
  select(-n) %>% 
  left_join(sau_spp)

# Get taxon at the genus level
genus_taxon <- sau_taxon_eez %>% 
  filter(is.na(dbem)) %>% 
  group_by(eezid,genus) %>% 
  tally() %>% 
  left_join(dbem_spp)
  
# Missing genus
genus_taxon_missing <- sau_taxon_eez %>% 
  filter(is.na(dbem)) 

genus_taxon_missing_list <- genus_taxon_missing %>% 
  pull(taxon_name) %>% 
  unique()
  

```


# 0. All the species in the world

## Matching genus overall

First we get SAU species that are not on the DBEM

```{r}

sau_taxon <- sau_catch %>% 
  group_by(taxon_key) %>% 
  tally() %>% 
  select(-n) %>% 
  left_join(sau_spp)

sau_taxon
```


```{r}

# Get sau SPP not in the DBEM at the genus level
sau_genus <- sau_taxon %>% 
  filter(is.na(dbem),
         !is.na(genus)) %>% 
  group_by(genus) %>% 
  tally() %>% 
  rename(n_spp = n)

dbem_genus <- sau_taxon %>% 
  filter(!is.na(dbem))

dbem_genus
  
```

Match those with the existing ones in the DBEM

```{r}

sau_dbem_genus <- sau_genus %>% 
  left_join(dbem_spp)

# for matching species
sau_genus_matching <-
  sau_taxon %>% 
  filter(is.na(dbem),
         !is.na(genus)) %>% 
  select(taxon_name_sau = taxon_name,
         taxon_key_sau = taxon_key,
         genus) %>% 
  left_join(dbem_spp) %>% 
  filter(!is.na(dbem)) 
  
```

There are still 287 genera that have not match with the DBEM these are... 

```{r}

sau_missing_gen <- sau_dbem_genus %>% 
  filter(is.na(dbem)) %>% 
  group_by(genus) %>% 
  tally()
  
sau_missing_gen

```

## Matching family overall

For those missing, we can match them at the family level... 

```{r}

sau_missing_fam <- sau_taxon %>% 
  filter(genus %in% sau_missing_gen$genus | is.na(genus))


sau_missing_fam_taxon <- sau_missing_fam %>% 
  filter(!is.na(taxon_name)) %>% 
  pull(taxon_name) %>% 
  unique()


# Get Family level for missing genus
class_fam_sau <- classification(sau_missing_fam_taxon, 
                           db = "worms",
                           best_match_only = TRUE,
                           ask = F) 

# Convert the list to a data frame
class_fam_sau_df <- map_dfr(class_fam_sau, ~as_tibble(.x), .id = "query") %>% 
  filter(rank == "Family") %>%
  # View()
  select(family = name,
         taxon_name = query)

# Get Family level for dbem
class_dbem <- classification(dbem_spp$taxon_name, 
                           db = "worms",
                           best_match_only = TRUE,
                           ask = F) 

# Convert the list to a data frame
calss_dbem_df <- map_dfr(class_dbem, ~as_tibble(.x), .id = "query") %>% 
  filter(rank == "Family") %>% 
  select(family = name,
         taxon_name = query) %>% 
  left_join(dbem_spp, "taxon_name")

```

Now we match the missing families together

```{r}
#Merge the families
sau_dbem_family <- class_fam_sau_df %>% 
  rename(taxon_name_sau = taxon_name) %>% 
  left_join(calss_dbem_df) %>% 
  filter(!is.na(dbem))
  
```

There are still about 183 missing taxa at the family level.

```{r}
#Merge the families
class_fam_sau_df %>% 
  rename(taxon_name_sau = taxon_name) %>% 
  left_join(calss_dbem_df) %>% 
  filter(is.na(dbem)) %>% 
  pull(taxon_name_sau) %>% 
  unique()
  
```


## Combine final data

DBEM column identifies the level of matching (`dbem_source`)
1 = species level (n = 915)
2 = genus level (n = 357)
3 = family level (n = 360)
NA = no match (n = 277)

```{r}
sau_taxon %>% 
  # mutate(dbem_g = ifelse(is.na(dbem) & genus %in% dbem_spp$genus,2,NA),
         # dbem_f = ifelse(is.na(dbem) & taxon_name %in% sau_dbem_family$taxon_name_sau,3,NA)
  # ) %>%
  mutate(dbem_source = 
                              ifelse(is.na(dbem) & genus %in% dbem_spp$genus,2,
                                     ifelse(is.na(dbem) & taxon_name %in% sau_dbem_family$taxon_name_sau,3,
                                            ifelse(dbem == 1, 1,NA)
                             )
  )
  ) %>% 
  select(1:4,dbem_source) %>% 
  filter(!is.na(taxon_name)) %>% 
  View()
  # write_csv("sau_general_dbem_source.csv")
  group_by(dbem_source) %>% 
  tally()

  
```

## Species - Genus relation data

```{r}

sub_df <- bind_rows(
  # Species to substitute at the genus level
  sau_genus_matching %>% mutate(dbem = 2) %>% select(taxon_name_sau,taxon_key_sau,taxon_name_dbem = taxon_name,taxon_key_dbem = taxon_key,dbem),
  # Species to substitute at the family level
  sau_dbem_family %>% select(taxon_name = taxon_name_sau,taxon_name_dbem = taxon_name,taxon_key_dbem = taxon_key) %>% left_join(sau_taxon) %>% 
    select(taxon_name_sau =taxon_name,taxon_key_sau = taxon_key,taxon_name_dbem,taxon_key_dbem) %>% 
    mutate(dbem = 3),
  # # Species at the species level
  sau_taxon %>% select(taxon_name_sau = taxon_name,taxon_key) %>% left_join(dbem_spp) %>% filter(dbem == 1) %>% select(taxon_name_sau,taxon_key_sau = taxon_key, taxon_name_dbem= taxon_name,dbem) %>% mutate(taxon_key_dbem = taxon_key_sau)
)

length(unique(sub_df$taxon_name_sau)) # 1632 taxa
length(unique(sau_taxon$taxon_name)) # 1910 taxa

# 1910-1632 = 278 missing


write_csv(sub_df,
          "sau_taxa_to_genus_family.csv")

```


# 1


```{r}





```


------



# 1. All the species in the EEZ

## Matching genus overall

First we get SAU species that are not in the DBEM

```{r}


sau_catch_eez <- sau_catch %>% 
  left_join(my_data("sau_index") %>% group_by(eezid=eez_id,eez_name) %>% tally()) %>% 
  group_by(eezid,eez_name,taxon_key) %>% 
  tally() %>% 
  select(-n) %>% 
  left_join(sau_spp)

dbem_sau_eez <- sau_catch %>%
  left_join(dbem_spp) %>% 
  filter(!is.na(dbem)) %>% 
  group_by(taxon_key,taxon_name,eez_name, eezid) %>% 
  tally() %>% 
  select(-n)

```


```{r}

# Get sau species that are not in the DBEM but are identified at the genus level
sau_genus <-
  sau_catch %>%
  filter(is.na(dbem),
         !is.na(genus)) %>% 
  group_by(eezid,eez_name,taxon_key,genus,dbem) %>% 
  tally() %>% 
  rename(n_spp = n)

# get sau taxons per eez that have DBEM data and genus
dbem_genus <- sau_catch %>%
  filter(!is.na(dbem))

dbem_genus
  
```

Match those with the existing ones in the DBEM

```{r}

# sau_dbem_genus <- sau_genus %>% 
  # left_join(dbem_sau_eez)

# for matching species
sau_genus_matching <-
  sau_genus %>% 
  filter(is.na(dbem),
         !is.na(genus)) %>% 
  select(eezid,
         eez_name,
        # sau_taxon_name = taxon_name,
         sau_taxon_key = taxon_key,
         genus) %>% 
  left_join(dbem_genus) %>% 
  filter(!is.na(dbem)) %>% 
  mutate(dbem = 2)
  
```

There are still 477 genera x eez that have not match with the DBEM these are... 

```{r}

sau_genus_missing_taxon <-
  sau_genus %>% 
  filter(is.na(dbem),
         !is.na(genus)) %>% 
  select(eezid,
         eez_name,
        # sau_taxon_name = taxon_name,
         sau_taxon_key = taxon_key,
         genus) %>% 
  left_join(sau_genus_matching) %>% 
  filter(is.na(dbem)) 
  
sau_genus_missing <- sau_genus_missing_taxon %>% 
  group_by(eez_name,genus) %>% 
  tally()
```

## Matching family overall

For those missing, we can match them at the family level... 

```{r}

# sau_missing_fam <- sau_taxon %>% 
  # filter(genus %in% sau_genus_missing_taxon$genus,
         # is.na(dbem))
 

# sau_missing_fam_taxon <- sau_missing_fam %>% 
#   filter(!is.na(taxon_name)) %>% 
#   pull(taxon_name) %>% 
#   unique()


# Get Family level for missing genus
class_fam_sau <- classification(sau_missing_fam_taxon, 
                           db = "worms",
                           best_match_only = TRUE,
                           ask = F) 

# Convert the list to a data frame
class_fam_sau_df <- map_dfr(class_fam_sau, ~as_tibble(.x), .id = "query") %>% 
  filter(rank == "Family") %>%
  # View()
  select(family = name,
         taxon_name = query)

# Get Family level for dbem
class_dbem <- classification(dbem_spp$taxon_name, 
                           db = "worms",
                           best_match_only = TRUE,
                           ask = F) 

# Convert the list to a data frame
calss_dbem_df <- map_dfr(class_dbem, ~as_tibble(.x), .id = "query") %>% 
  filter(rank == "Family") %>% 
  select(family = name,
         taxon_name = query) %>% 
  left_join(dbem_spp, "taxon_name")

```

Now we match the missing families together

```{r}

sau_genus_missing %>% 
  left_join()

fam_sub_df <- sub_df %>% filter(dbem == 3)



#Merge the families

sau_dbem_family <- sau_missing_fam %>% 
  rename(taxon_name_sau = taxon_name,
         taxon_key_sau = taxon_key) %>% 
  select(-dbem) %>% 
  left_join(fam_sub_df) %>%
  filter(!is.na(dbem))
  
  
```



## Combine final data

DBEM column identifies the level of matching (`dbem_source`)
1 = species level (n = 915)
2 = genus level (n = 357)
3 = family level (n = 360)
NA = no match (n = 277)

```{r}
sau_taxon %>% 
  # mutate(dbem_g = ifelse(is.na(dbem) & genus %in% sau_genus_matching$genus,2,NA),
  # dbem_f = ifelse(is.na(dbem) & taxon_name %in% sau_dbem_family$taxon_name_sau,3,NA)
  # ) %>%
  mutate(dbem_source =
                              ifelse(is.na(dbem) & genus %in% sau_genus_matching$genus,2,
                                     ifelse(is.na(dbem) & taxon_name %in% sau_dbem_family$taxon_name_sau,3,
                                            ifelse(dbem == 1, 1,NA)
                             )
  )
  ) %>%
  select(1:4,dbem_source) %>%
  filter(!is.na(taxon_name)) %>% 
  # View()
  # write_csv("sau_eez_dbem_source.csv")
  group_by(dbem_source) %>% 
  tally()

  
```


## Species - Genus relation data

```{r}

sub_df <- bind_rows(
  # Species to substitute at the genus level
  sau_genus_matching %>% mutate(dbem = 2) %>% select(taxon_name_sau,taxon_key_sau,taxon_name_dbem = taxon_name,taxon_key_dbem = taxon_key,dbem),
  # Species to substitute at the family level
  sau_dbem_family %>% select(taxon_name = taxon_name_sau,taxon_name_dbem = taxon_name,taxon_key_dbem = taxon_key) %>% left_join(sau_taxon) %>% 
    select(taxon_name_sau =taxon_name,taxon_key_sau = taxon_key,taxon_name_dbem,taxon_key_dbem) %>% 
    mutate(dbem = 3),
  # # Species at the species level
  sau_taxon %>% select(taxon_name_sau = taxon_name,taxon_key) %>% left_join(dbem_spp) %>% filter(dbem == 1) %>% select(taxon_name_sau,taxon_key_sau = taxon_key, taxon_name_dbem= taxon_name,dbem) %>% mutate(taxon_key_dbem = taxon_key_sau)
)

length(unique(sub_df$taxon_name_sau)) # 1632 taxa
length(unique(sau_taxon$taxon_name)) # 1910 taxa

# 1910-1632 = 278 missing


write_csv(sub_df,
          "sau_taxa_to_genus_family.csv")

```



# Share Per Change Data


```{r}

files_list <- my_path("R",extra_path = "mcp_nutrition",list_files = "paths")


for(i in 1:length(files_list)){

    file_to_read <- files_list[i]
  
  
  read_csv(file_to_read) %>% 
    select(-sd_mcp) %>% 
    pivot_wider(names_from = "period",values_from = "mean_mcp") %>% 
    mutate(
      per_change = my_chng(present_1995_2014,mid_2020_2039)
    ) %>% 
    select(taxon_key,eez_name,ssp,per_change) %>% 
    write_csv(
      .,
      paste0(str_sub(file_to_read,1,str_count(file_to_read)-6),"perchng.csv")
    )
  
}




```



